figures_manuscript

### 2025-07-17 pub_figures/manuscript-figures.Rmd
annotation xls

# of shrinked results
total <- subset(res, padj< 0.05) %>% nrow()
up <- subset(res, padj< 0.05 & log2FoldChange > 1) %>% nrow()
down <- subset(res, padj< 0.05 & log2FoldChange < -1) %>% nrow()

# of "true" results
total <- subset(res_n, padj< 0.05) %>% nrow()
up <- subset(res_n, padj< 0.05 & log2FoldChange > 1) %>% nrow()
down <- subset(res_n, padj< 0.05 & log2FoldChange < -1) %>% nrow()

@@

# of "true" results
total <- subset(res_n, padj< 0.05) %>% nrow()
up <- subset(res_n, padj< 0.05 & log2FoldChange > 1) %>% nrow()
down <- subset(res_n, padj< 0.05 & log2FoldChange < -1) %>% nrow()

@@

colnames(anno)
anno[deg_list$pcry$deg_pcry_RvD.vs.WT_RvD,]
anno[deg_list$pcry$deg_pcry_RvD.vs.WT_RvD,c("geneSymbol","previousIdentifiers","Description","previousIdentifiers","Description","Comments","TMHMM_transmembrane","TargetP","Predalgo","Flagellar_Proteome")] %>% kable()

@@

gg_phots <- ggplot(df, aes(x=l2FC.WT_blue, y=l2FC.WT_red, label=symbol)) + # color=group, fill=group 
    geom_segment(aes(x = l2FC.WT_blue, y= l2FC.WT_red, xend = l2FC.pcry_blue,yend = l2FC.pcry_red, color = l2FC.dd_red),
        arrow = arrow(length = unit(0.01,units = "npc"))) +
  scale_color_gradient2(mid="grey") +
  geom_point(shape=21, fill="grey", col="grey40") +
  geom_point(aes(x=l2FC.pcry_blue, y=l2FC.pcry_red),shape=21, fill="green3", col="grey40") +
  geom_hline(yintercept = c(-1,1), linewidth = 0.1) + 
  geom_vline(xintercept = c(-1,1), linewidth = 0.1) +
  geom_abline(slope=c(1), intercept = 0, linewidth = 0.1) +
  # coord_cartesian(xlim=c(-5,5),ylim = c(-5,5)) +
  coord_fixed() +
  geom_text_repel(size=4, max.overlaps = 20) +
  theme_bw() +
  removeGrid(x=T, y=T)
gg_phots

@@

# TOP
df <- res_comb[blue_red_genes,]

@@

>>>>

# of shrinked results
total <- subset(res, padj< 0.05 & (log2FoldChange > 1 | log2FoldChange < -1 )) %>% nrow()
up <- subset(res, padj< 0.05 & log2FoldChange > 1) %>% nrow()
down <- subset(res, padj< 0.05 & log2FoldChange < -1) %>% nrow()

# of "true" results
total <- subset(res_n, padj< 0.05 & (log2FoldChange > 1 | log2FoldChange < -1 )) %>% nrow()
up <- subset(res_n, padj< 0.05 & log2FoldChange > 1) %>% nrow()
down <- subset(res_n, padj< 0.05 & log2FoldChange < -1) %>% nrow()

@@

# of "true" results
total <- subset(res_n, padj< 0.05 & (log2FoldChange > 1 | log2FoldChange < -1 )) %>% nrow()
up <- subset(res_n, padj< 0.05 & log2FoldChange > 1) %>% nrow()
down <- subset(res_n, padj< 0.05 & log2FoldChange < -1) %>% nrow()

@@

colnames(anno)
# anno[deg_list$pcry$deg_pcry_RvD.vs.WT_RvD,]
anno[deg_list$pcry$deg_pcry_RvD.vs.WT_RvD,c("geneSymbol","previousIdentifiers","Description","previousIdentifiers","Description","Comments","TMHMM_transmembrane","TargetP","Predalgo","Flagellar_Proteome")] %>% kable()

@@

gg_phots <- ggplot(df, aes(x=l2FC.WT_blue, y=l2FC.WT_red, label=symbol)) + # color=group, fill=group 
    geom_segment(aes(x = l2FC.WT_blue, y= l2FC.WT_red, xend = l2FC.pcry_blue,yend = l2FC.pcry_red, color = l2FC.dd_red),
        arrow = arrow(length = unit(0.01,units = "npc"))) +
  scale_color_gradient2(mid="grey") +
  geom_point(shape=21, fill="grey", col="grey40") +
  geom_point(aes(x=l2FC.pcry_blue, y=l2FC.pcry_red, fill = "pcry"),shape=21, col="grey40") +
  scale_fill_manual(name="Genotype",values="green3") +
  geom_hline(yintercept = c(-1,1), linewidth = 0.1) + 
  geom_vline(xintercept = c(-1,1), linewidth = 0.1) +
  geom_abline(slope=c(1), intercept = 0, linewidth = 0.1) +
  # coord_cartesian(xlim=c(-5,5),ylim = c(-5,5)) +
  coord_fixed() +
  geom_text_repel(size=4, max.overlaps = 20) +
  theme_bw() +
  removeGrid(x=T, y=T)
gg_phots

@@

# TOP
df <- res_comb[blue_red_genes,]
df %>% kable()

plot(df$l2FC.dd_red ~ df$l2FC.dd_blue)

@@

  scale_colour_manual(name="Error Bars",values=cols)
